Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-04 tex/covidEffectOfNPI-revision.tex
update

We  also consider simple counterfactual exercises, where we examine the effects of setting
a sequence of counterfactual policies for each state:
\begin{equation} \label{p-cf}\tag{P-CF}
\{{\pcolor P^\star_{it}} \}_{t=1}^T, \quad i=1, \ldots N.
\end{equation}
We assume that the SEM remains invariant, except for the policy equation.\footnote{It is possible to consider counterfactual exercises in which policy  responds to information through the policy equation if we are interested in endogenous policy responses to information. Although this is beyond the scope of the current paper, counterfactual experiments with endogenous government policy would be important, for example, to understand the issues related to the lagged response of government policies to higher infection rates due to incomplete information. } Given the policies, we generate the counterfactual
outcomes, behavior, information by propaging the dynamic equations:
\begin{equation} \label{eqn:CF-SEM} \tag{CEF-SEM}
  \begin{aligned}
& {\ycolor Y^\star_{i,t+\ell}}  & := & Y_{i,t+\ell} ( {\bcolor B^\star_{it} } , {\pcolor P^\star_{it}}, {\icolor I^\star_{it}}), \\
& {\bcolor B^\star_{it} } & := &   B_{it}({\pcolor P^\star_{it} } ,{\icolor I^\star_{it}}), \\
& {\icolor I^\star_{it} }& := &  I ({ t,  {\ycolor Y^\star_{it}}, \icolor I^\star_{i,t-\ell}}),  \end{aligned}
\end{equation}
with the same initialization as the factual system up to $t \leq 0$. In stating this counterfactual system of equations, we assume that structural outcome equations (SO) and information equations (I) remain invariant, and so do the stochastic shocks, decomposed
into observable and unobservable parts. Formally, we record this assumption and above discussion as follows.

>>>>

We  also consider simple counterfactual exercises, where we examine the effects of setting
a sequence of counterfactual policies for each state:
\begin{equation} \label{p-cf}\tag{P-CF}
\{{\pcolor P^\star_{it}} \}_{t=1}^T, \quad i=1, \ldots N.
\end{equation}
We assume that the SEM remains invariant, except for the policy equation.\footnote{It is possible to consider counterfactual exercises in which policy  responds to information through the policy equation if we are interested in endogenous policy responses to information. Counterfactual experiments with endogenous government policy would be important, for example, to understand the issues related to the lagged response of government policies to higher infection rates due to incomplete information. } Given the policies, we generate the counterfactual
outcomes, behavior, information by propaging the dynamic equations:
\begin{equation} \label{eqn:CF-SEM} \tag{CEF-SEM}
  \begin{aligned}
& {\ycolor Y^\star_{i,t+\ell}}  & := & Y_{i,t+\ell} ( {\bcolor B^\star_{it} } , {\pcolor P^\star_{it}}, {\icolor I^\star_{it}}), \\
& {\bcolor B^\star_{it} } & := &   B_{it}({\pcolor P^\star_{it} } ,{\icolor I^\star_{it}}), \\
& {\icolor I^\star_{it} }& := &  I ({ t,  {\ycolor Y^\star_{it}}, \icolor I^\star_{i,t-\ell}}),  \end{aligned}
\end{equation}
with the same initialization as the factual system up to $t \leq 0$. In stating this counterfactual system of equations, we assume that structural outcome equations (SO) and information equations (I) remain invariant, and so do the stochastic shocks, decomposed
into observable and unobservable parts. Formally, we record this assumption and above discussion as follows.
